Binary companions of red giant stars with APOGEE DR14

### 2018-02-23 paper/1-catalog/twoface-catalog.tex
Restructure results to be more to-the-point

\subsection{Initial individual-system posterior samplings}
\label{sec:initsampling}

For all \nstars\ \apogee\ stars with $\geq 3$ good visits (see
\sectionname~\ref{sec:data}), we use \thejoker\ to generate posterior samplings
for each star under the assumptions listed above (see
\sectionname~\ref{sec:fitting}).
We start by generating a library of \nprior\ prior samples generated under a
prior similar to that defined in \citet{Price-Whelan:2017}:
\begin{itemize}
    \item uniform or isotropic in angle parameters,
    \item uniform in log-period over the domain $[1,32768]~\textrm{day}$,
    \item a beta distribution over eccentricity with fixed parameters (\citealt{Kipping:2013}).
\end{itemize}
For the prior over the excess variance parameter, $s^2$, we initially use
a Gaussian over the transformed parameter $y = \ln s^2$ with the mean and
standard deviation of the initial distribution set to $(\mu_{y,0}, \sigma_{y,0})
= (10.6, 3)$ in units of $\textrm{m}~\textrm{s}^{-1}$.
The reference time for each star is set to the minimum visit epoch; $M_0$ then
becomes the mean anomaly at the first visit observation.
See \tablename~\ref{tbl:params} for a description of all parameters and priors
used.

@@

We request \nposterior\ posterior samples for each source.
Depending on the data quality and phase coverage of the visits, \thejoker\ will
require different numbers of prior samples in order to rejection sample down to
the requested number of posterior samples: For few-epoch or noisy RV data, many
prior samples will pass the rejection step, whereas for very precise or
many-epoch RV data, \thejoker\ may need to go process the full library of prior
samples.
We therefore generate the posterior samples using an iterative procedure that
adaptively predicts how many prior samples to test for each star.
For sources with very constraining data, \thejoker\ may return fewer than the
requested number of samples (as few as one sample).
When this happens, we proceed in one of two ways:
\begin{enumerate}
    \item \emph{needs MCMC}: If just 1 posterior sample is returned after
    exhausting the full library of prior samples, or if multiple (but fewer than
    \nposterior) are returned that all lie within a single mode of the posterior
    pdf, the posterior pdf over orbital parameters is treated as effectively
    unimodal.
    In this case, we use the location of the returned sample, or the median over
    returned samples to generate a small ball of initial conditions and use
    standard MCMC to continue sampling until we obtain \nposterior\ samples.
    In detail, we use an ensemble sampler (\citealt{Goodman:2010}) implemented
    in \python\ (\citealt{Foreman-Mackey:2013}) for this step.
    We run with 1024 walkers for 16384 steps, take the final walker positions,
    and downsample until we have \nposterior\ samples.
    We compute convergence statistics for each run and report whether the chains
    appear converged or not.
    \item \emph{needs more prior samples}: If more than 1 posterior sample is
    returned after exhausting the full library of prior samples and the samples
    lie in multiple modes of the posterior pdf, the star is flagged. In this
    case, the only way to proceed is to generate more prior samples and continue
    running \thejoker\ for these sources to generate more posterior samples.
\end{description}

A full run of \thejoker\ on all \nstars\ \apogee\ stars used in this work took
approximately 300 hours on a compute cluster with 448 cores, with the time
dominated by sources with many ($\gtrsim 10$) visits.
\todo{XX} stars were flagged as \emph{needs MCMC}, \todo{YY} were flagged as
\emph{needs more prior samples}, and the remaining \todo{ZZ} stars completed normally.

@@

\section{Results}

@@

@@

In detail, we maximize the marginal likelihood of the population-level
parameters $\bs{\alpha} = (\mu_y, \sigma_y)$.
We compute this marginal likelihood using the per-object posterior samples
re-weighted by the ratio of the value of the hyperprior evaluated at a given
vector $\bs{\alpha}$ over the value of the default prior at the previously
assumed values, $\bs{\alpha}_0 = (\mu_{y,0}, \sigma_{y,0})$ (see
\sectionname~\ref{sec:initsampling}).
This trick has been used in other hierarchical inferences as a way to
marginalize over the per-object parameters
(\citealt{Hogg:2010,Foreman-Mackey:2014}); we describe how to compute the
marginal likelihood in detail below.

@@

We use 1,825 stars with $>10$ visits and $\log g < 2$ (to avoid upper RGB stars
that have large intrinsic jitter) and maximize the above likelihood to determine
better hyperparameters for the log-excess-variance parameter distribution.
\figurename~\ref{fig:infer-jitter} shows the distribution corresponding to the
maximum-likelihood hyperparameters, $\alpha^* = (\mu_y^*, \sigma_y^*) = (9.50,
1.64)$.
\todo{Reactions to the inferred parameters?}
\todo{Discuss how this relates to empirical Bayes?}

@@

TODO: re-do exactly \sectionname~\ref{sec:initsampling}, but with $(\mu_{y}, \sigma_{y}) = (9.5, 1.6)$ again in units of ${\rm m}~{\rm s}^{-1}$.

TODO: how many hit each category (flag) after the initial run

@@

\todo{APW}

Thresholding on what now?

Catalog.

Some highlights from this catalog.

@@

\software{
The code used in this project is available from
\url{https://github.com/adrn/TwoFace} under the MIT open-source
software license.
This research utilized the following open-source \python\ packages:
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    % \package{corner} (\citealt{Foreman-Mackey:2016}),
    % \package{emcee} (\citealt{Foreman-Mackey:2013ascl}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}).
}

>>>>

\subsection{Individual-system posterior samplings}
\label{sec:initsampling}

\todo{Explain that this is the procedure, but two full runs described below in results...}

For all \nstars\ \apogee\ stars with $\geq 3$ good visits (see
\sectionname~\ref{sec:data}), we use \thejoker\ to generate posterior samplings
for each star under the assumptions listed above (see
\sectionname~\ref{sec:fitting}).
We start by generating a library of \nprior\ prior samples generated under a
prior similar to that defined in \citet{Price-Whelan:2017}:
\begin{itemize}
    \item uniform or isotropic in angle parameters,
    \item uniform in log-period over the domain $[1,32768]~\textrm{day}$,
    \item a beta distribution over eccentricity with fixed parameters (\citealt{Kipping:2013}).
\end{itemize}
For the prior over the excess variance parameter, $s^2$, we initially use
a Gaussian over the transformed parameter $y = \ln s^2$ with the mean and
standard deviation $(\mu_y, \sigma_y)$ indicated where the runs are described
(see \sectionname~\ref{sec:results}).
The reference time for each star is set to the minimum visit epoch; $M_0$ then
becomes the mean anomaly at the first visit observation.
\tablename~\ref{tbl:params} contains descriptions of all parameters and priors
used.

@@

We request \nposterior\ posterior samples for each source.
Depending on the data quality and phase coverage of the visits, \thejoker\ will
require different numbers of prior samples in order to rejection sample down to
the requested number of posterior samples: For few-epoch or noisy RV data, many
prior samples will pass the rejection step, whereas for very precise or
many-epoch RV data, \thejoker\ may need to go process the full library of prior
samples.
We therefore generate the posterior samples using an iterative procedure that
adaptively predicts how many prior samples to test for each star.
For sources with very constraining data, \thejoker\ may return fewer than the
requested number of samples (as few as one sample).
If just 1 posterior sample is returned after exhausting the full library of
prior samples, or if multiple (but fewer than \nposterior) are returned that all
lie within a single mode of the posterior pdf, the posterior pdf over orbital
parameters is treated as effectively unimodal: these stars are flagged ``needs
MCMC.''
If more than 1 posterior sample is returned after exhausting the full library of
prior samples, and the samples lie in multiple modes of the posterior pdf, the
only way to proceed is to generate more prior samples and continue running
\thejoker: these stars are flagged ``needs more prior samples.''

\subsubsection{``Needs MCMC'': Following up \thejoker\ with MCMC}

In this case, we use the location of the returned sample, or a randomly chosen
sample from those returned to generate a small ball of initial conditions and
use standard MCMC to continue sampling until we obtain \nposterior\ samples.

We use an ensemble MCMC sampling algorithm (\citealt{Goodman:2010}) implemented
in \python\ (\citealt{Foreman-Mackey:2013}) for this step.
We run with 1024 walkers for 16384 steps, take the final walker positions, and
downsample until we have \nposterior\ samples.
\todo{We compute convergence statistics for each run and report whether the
chains appear converged or not.}

\subsubsection{``Needs more prior samples'': Continuing \thejoker\ sampling}

We generate another equal-sized library of prior samples (a total of
$2\times\nprior$ samples) and continue sampling.
\todo{We note that because ... rejection sampling procedure, have to re-do
the rejection step after computing with full library of samples...}

@@

\section{Results}
\label{sec:results}

@@

A full run of \thejoker\ on all \nstars\ \apogee\ stars used in this work took
approximately 300 hours on a compute cluster with 448 cores, with the time
dominated by sources with many ($\gtrsim 10$) visits.

For this initial run, we do not follow up on stars that return $<$\nposterior\
samples.

of the initial distribution set to $(\mu_{y,0}, \sigma_{y,0})
= (10.6, 3)$ in units of $\textrm{m}~\textrm{s}^{-1}$.

@@

\todo{Move math to appendix since we cite relevant papers that show how?}
In detail, we maximize the marginal likelihood of the population-level
parameters $\bs{\alpha} = (\mu_y, \sigma_y)$.
We compute this marginal likelihood using the per-object posterior samples
re-weighted by the ratio of the value of the hyperprior evaluated at a given
vector $\bs{\alpha}$ over the value of the default prior at the previously
assumed values, $\bs{\alpha}_0 = (\mu_{y,0}, \sigma_{y,0})$ (see
\sectionname~\ref{sec:initsampling}).
This trick has been used in other hierarchical inferences as a way to
marginalize over the per-object parameters
(\citealt{Hogg:2010,Foreman-Mackey:2014}); we describe how to compute the
marginal likelihood in detail below.

@@

We use 1,825 stars with $>10$ visits and $\log g < 2$ (to avoid upper RGB stars
that have large intrinsic jitter) and maximize the above likelihood to determine
better hyperparameters for the log-excess-variance parameter distribution.
\figurename~\ref{fig:infer-jitter} shows the distribution corresponding to the
maximum-likelihood hyperparameters, $\alpha^* = (\mu_y^*, \sigma_y^*) = (9.50,
1.64)$.
\todo{Reactions to the inferred parameters?}

@@

Using the maximum-likelihood hyperparameters derived from the initial posterior
samplings (see \sectionname~\ref{sec:initsampling}), we update and fix the
excess variance prior distribution parameters---$(\mu_{y}, \sigma_{y}) = (9.5,
1.6)$ in units of $\textrm{m}~\textrm{s}^{-1}$---and re-run \thejoker\ on the
parent sample of \apogee\ \DR\ stars.
\todo{Discuss how this relates to empirical Bayes?}

From this run, 91,096 stars completed and successfully returned \nposterior\
samples using \thejoker\ alone.
The remaining 5,135 stars did not return \nposterior\ samples: 4,744 were
flagged as \emph{needs more prior samples}, 391 as \emph{needs MCMC}.

@@

\todo{Thresholding on what now?}

\todo{Some highlights from this catalog.}

@@

\software{
% The code used in this project is available from
% \url{https://github.com/adrn/TwoFace} under the MIT open-source
% software license.
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    % \package{corner} (\citealt{Foreman-Mackey:2016}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}).
}
